Communicating human related spatial distributions: A comparison of spatial visualisations using visual inference.

### 2020-01-07 paper/paper.Rmd
beeswarm plot

>>>>

```{r eval=FALSE}
# Di playing
s <- d %>% group_by(type, trend, detect) %>%
  summarise(m=median(time_taken), 
            q1=quantile(time_taken, 0.25), 
            q3=quantile(time_taken, 0.75))
library(ggbeeswarm)
ggplot() + 
  geom_quasirandom(data=d, aes(x=type, y=time_taken), alpha=0.9) + 
  #geom_hline(data=s, aes(yintercept=m, colour=type)) +
  geom_point(data=s, aes(x=type, y=m, colour=type), size=5, alpha=0.7) +
  #geom_errorbar(data=s, aes(x=type, ymin=q1, ymax=q3, colour=type), width=0.3, size=2) +
  scale_colour_brewer(palette = "Dark2") +
  facet_grid(trend~detect)
```
